%---------------------------------------------------------------------------%
%->> Frontmatter
%---------------------------------------------------------------------------%

\maketitle
\MAKETITLE
\makedeclaration



\intobmk\chapter*{摘\quad 要}
\setcounter{page}{1}
\pagenumbering{Roman}.  %Chinese abstract 
\addcontentsline{toc}{chapter}{摘\quad 要} %Add abstract to table of contents

众所周知，第一代恒星 是在高红移的低质量晕圈中形成的。这些恒星物体的典型质量（M $ _ {\star} \sim 100 $ M  $_{\odot} $）与现今的恒星相比更高; 由于没有足够的冷却剂。 然而，这些短命的恒星在它们爆炸并用重金属（例如碳和氧）污染周围的原始气体时，已经戏剧性地改变了这幅画面。 提供有效气体冷却的途径，从而允许形成低质量和中质量恒星。 因此，推测Pop III恒星的后代显示出独特的丰度模式（相当低的铁和高度增强的碳）。


在这项研究中，我们提出12种金属贫乏恒星的化学成分和运动参数，在银河系光环系统的金属度范围为 $-3.3 <$ [Fe / H] $ < -  2.4 $。这个恒星样本最初被确定为LAMOST DR3低分辨率（R $ \sim $ 2,000）中的金属贫乏候选者。 Lick / APF获得高分辨率（R $ \equiv \lambda / \Delta \lambda \sim $ ~110,000）光谱观察。我们确定了恒星参数（\ensuremath{T_\mathrm{eff}}，\ensuremath{\log\,g}，[Fe/H]和$\xi$）以及最多25个元素的个体丰度：包括碳和氮，光（Na-Ca），铁 - 峰（Sc-Zn）和多达11个中子俘获元素（包括Ba和Eu），以定量评估我们的tagret星。我们的样本恒星的化学丰度模式显示我们的样本包含五个碳正常恒星和七个碳增强金属贫乏（CEMP）恒星：（i）CEMP-r / s恒星J2114$-$0616 [C/Fe]=1.37，[N/Fe] = 1.88，[Ba/Fe] = 1.00，[Eu/Fe] = 0.84，（ii）CEMP-r星J1054 + 0528，[C/Fe]=0.82，[Eu/Fe]=0.44和[Ba/Fe]=$-$0.52（iii）CEMP-no（ [C/Fe]$\geqslant+0.7$和[Ba/Fe]$<0.0$）明星J1529+0804，J1630+0953，J1645+4357，J2216+0246和J2216+2232。此外，观察到的光和重元素的化学丰度表明我们的目标恒星可能是由混合良好的恒星云产生的。


此外，我们使用两个CEMP-no星（J1630+0953和J2216+0246）的光元素丰度与零金属度超新星模型进行蒙特卡罗模拟比较，产生 $10^{4}$ 生成集，以推断质量CEMP恒星的恒星祖先的分布。对于J1630+0953的情况，绝大多数这些集合（$ \ sim~94 \％$）与预测的祖先产量相匹配，恒星质量范围为21-25M$_{\odo}$和爆炸能量 $0.3 \times 10^{51}$erg。
其余的这些生成组（600组）显示，恒星质量为50 M$_{\odot}$和爆炸能量为 $10.0\times 10^{51}$ erg的祖先可能是造成污染的原因。 J1630 + 0953诞生云。 J2216 + 0246的采样集周围的$\sim ~85\％$ 表明在J2216+0246大气中携带的观测元素模式对应于恒星质量范围为13-16 M$_{\odot}$和爆炸能量$ 1.5 $-$ 1.8\times 10^{51}$ erg。然而，在大约$\sim~15\％$的J2216+0246生成的套装匹配更重的恒星质量范围（10.6-29.5 M$_{\odot}$）和更强的爆炸能量（$0.6$-$5\times 10^{51} $ erg）。一般而言，这种蒙特卡罗模拟练习表明，这些巨大恒星祖先的化学产量污染了J1630+0953和J2216+0246的出生云，然后提供冷却途径以允许形成这些CEMP-no恒星。此外，这些可能的祖先（恒星质量范围为13-25 M$_{\odot} $和爆炸能量为0.3-1.8$ \times 10^{51}$ erg)
可以解决第一代恒星的初始质量函数。
与此同时，他们提出了另一个问题，即无论是否更大规模的SN，它可能会更加精力充沛，消灭主机晕云并且不允许形成EMP星。

为了完整起见，我们根据最近发表的Gaia DR2观测结果对我们的样本恒星进行了运动学和动力学分析。 这个练习的结果（运动参数，恒星轨道和结合能）表明我们的样本只包含一个外部晕星（J2114 $-$ 0616），而我们的其他样本恒星可能是内晕星，但是有一个增生 起源。 此外，我们的样本恒星的巨大主体距离银河系中心的距离接近$ \sim $ 2.9 kpc。


一般来说，这项研究试图将我们的样本恒星的衍生丰度模式与源自盖亚DR2观测的运动学相关联，从而对起源和
CEMP恒星的化学演化，以及对银河系中最低金属度恒星的群体III祖先的性质的严格限制。


\keywords{银河系：光环---恒星：基本参数---恒星：丰度----恒星：运动学和动力学---恒星：人口II ---恒星：化学特殊} %Chinese keywords


\intobmk\chapter*{Abstract} %English abstract.
\addcontentsline{toc}{chapter}{Abstract} % Add abstract to table of contents

It is widely recognized that the very first-generation of stars (Population III or Pop III) have formed in low-mass halos at high-redshifts. The typical mass of these stellar objects ($10 - 1000$ M$_{\odot}$) indicates the absence of sufficient cooling agents. However, these short-lived stars had dramatically changed this picture by the time hey exploded and polluted the surrounding pristine gas with heavy metal (e.g., carbon); providing pathways for efficient gas cooling, and thus allowing the low- and intermediate-mass stars to form. As a result, the progeny of Pop III stars are presumed to show unique abundance patterns (low iron abundances with high with carbon enhancement). 


In this study, we present chemical compositions and kinematic parameters of 12 stars in the metallicity range of $-3.3<$  [Fe/H] $<-2.4$ in the Milky Way halo system. This sample of stars was first identified as metal-poor candidates in the LAMOST DR3 low-resolution (R$ \sim$ 2,000). High-resolution (R $\equiv \lambda /\Delta \lambda \sim$ ~ 110,000) spectroscopic observations were obtained by the Lick/APF. We determined stellar parameters (\ensuremath{T_\mathrm{eff}}, \ensuremath{\log\,g}, [Fe/H], and $\xi$) and individual abundances for up to 25 elements: include carbon and nitrogen, light (Na-Ca), iron-peak (Sc-Zn), and up to 11 neutron-capture elements (including Ba and Eu), to quantitatively evaluate our tagret stars. The chemical abundance patterns of our sample stars reveal that our sample contain five carbon normal stars and seven carbon-enhanced metal-poor (CEMP) stars: (i)The CEMP-r/s star J2114$-$0616 with [C/Fe]=1.37,  [N/Fe]= 1.88, [Ba/Fe]=1.00, and [Eu/Fe]=0.84, (ii) The CEMP-r star J1054+0528 with [C/Fe]=0.82, [Eu/Fe]=0.44 and [Ba/Fe]=$-$0.52 (iii) The CEMP-no ([C/Fe] $\geqslant +0.7$ and [Ba/Fe] $< 0.0$) stars J1529+0804, J1630+0953, J1645+4357, J2216+0246, and J2216+2232. Besides, the observed chemical abundances of the light and the heavy elements indicate that our target stars might likely be born from a well-mixed stellar cloud. 


In addition, we performed Monte Carlo simulations comparison of $10^{4}$ sets, using the light-element abundances of two CEMP-no stars (J1630+0953 and J2216+0246) with zero-metallicity supernova models to infer the mass distribution of the stellar progenitors of CEMP stars. For the case of J1630+0953, the majority of these sets ($\sim 94\%$) matches the predicted yields of a progenitor with a stellar-mass range of 21-25 M$_{\odot}$ and explosion energy of $0.3 \times 10^{51}$ erg. The rest of these generated sets (600 sets) shows that a progenitor with a stellar mass of 50 M$_{\odot}$ and explosion energy of $10.0 \times 10^{51}$ erg is likely responsible for the contamination of the J1630+0953 birth cloud. Around $85\%$ of the sampled sets of J2216+0246 suggest that the observed elemental pattern carried in J2216+0246 atmosphere correspond to a progenitor with a stellar-mass range of 13-16 M$_{\odot}$ and explosion energy of $1.5$-$1.8 \times 10^{51}$ erg. However, in about $15\%$ of J2216+0246 generated sets matches heavier stellar-mass range (10.6-29.5 M$_{\odot}$) and stronger explosion energies ($0.6$-$5 \times 10^{51}$ erg). In general terms, this Monte Carlo simulations exercise indicates that chemical yields of these massive stellar progenitors polluted the birth cloud of J1630+0953 and J2216+0246, which then provided cooling pathways to allow the formation of these CEMP-no stars. Moreover, these possible progenitors (stellar-mass range of 13-25 M$_{\odot}$ and explosion energies of 0.3-1.8$ \times 10^{51}$ erg) 
may address the initial mass function of the very first stellar generation. 
At the same time, they raise another question whether or not more massive SN, which in term might be more energetic, wipeout the host halo cloud and not permit the formation of EMP stars.

For completeness, we conducted a kinematic and dynamical analysis for our sample stars based on the recently published observations of Gaia DR2. The results of this exercise (kinematic parameters, stellar orbits, and binding energy) indicate that our sample contains only one outer halo star (J2114$-$0616), while the rest of our sample stars are likely inner halo stars, but with an accreted origin. Also, the vast majority of our sample stars, pass close to the Galactic center ($\sim 2.9$ kpc). 


In general, this study attempts to attach two cosmological solutions ( the derived abundance patterns of our sample stars and the kinematics derived from Gaia DR2 observations) to place crucial limitations on the origin and
chemical evolution of CEMP stars, together with critical constraints on the nature of the Population III progenitors of the lowest metallicity stars in our Galaxy.










\KEYWORDS{Galaxy: halo--- stars:fundamental parameters--- stars: abundances----stars: kinematics and dynamics --- stars: Population II--- stars: chemically peculiar} %English keywords
%---------------------------------------------------------------------------%
